$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-04-30 paper/paper.tex
Move a lemma so that it precedes the theorem that depends on it

@@

    \item
    Finally, in the $\constr{struct}$ case, we apply subject congruence (Theorem \ref{thm:subject-congruence}) and then the induction hypothesis.
  \end{itemize}
\end{proof}

\begin{nilemma}
  \label{lm:comm-capable}
  Every input usage context $\Gamma$ on a well-typed process $\types{\gamma}{\Gamma}{P}{\Delta}$ that reduces such that $P \reduce{\constr{external} \; i} Q$ has a multiplicity of at least $\lio$ at index $i$.
\end{nilemma}
\begin{proof}
  By induction on the reduction derivation $P \reduce{\constr{external \; i}}Q$.
\end{proof}

>>>>

\begin{nilemma}
  \label{lm:comm-capable}
  As an auxiliary lemma, we must establish that every input usage context $\Gamma$ of a well-typed process $\types{\gamma}{\Gamma}{P}{\Delta}$ that reduces by communicating on a channel external to it (that is, $P \reduce{\constr{external} \; i} Q$ for some $Q$) has a multiplicity of at least $\lio$ at index $i$.
\end{nilemma}

\begin{proof}
  By induction on the reduction derivation $P \reduce{\constr{external \; i}}Q$.
\end{proof}

@@

    \item
    Finally, in the $\constr{struct}$ case, we apply subject congruence (Theorem \ref{thm:subject-congruence}) and the induction hypothesis.
  \end{itemize}
\end{proof}
